Status of nuclear optical potentials and future prospects

### 2019-07-26 Notes/Candidacy/Paper/candidacy_paper.tex
Updates to candidacy paper
Added some sub-sections.
Updated candidacy paper
First draft complete. Added revisions to all sections outside of conclusion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: candidacy_paper.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: July 1, 2019
%
% Candidacy paper on the status of nuclear optical potentials and future prospects.
%
% Revision history:
% 	07/02/19 --- Starting with bulleted outline.
%     07/10/19 --- Adding equations to formalism section.
%	07/11/19 --- Put theoretical issues section as part of the conclusion. Also, wrote much of the formalism section.
%	07/15/19 --- Wrote the phenomenology section.
%	07/17/19 --- Wrote the introduction section.
%	07/19/19 --- Wrote microscopic optical potentials section.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Nuclear reactions are central to many areas of physics. A good understanding of these processes is necessary to answer questions such as the origin of the heavy elements in the universe, fundamental symmetries, or the limits of nuclear stability. For example, half of the neutron-rich atomic nuclei past iron on the periodic table are created by the rapid neutron-capture process known as the r-process which involves a series of nuclear reactions even with nuclei that have never been experimentally produced. Construction of an ``r-process laboratory'' is underway, the Facility for Rare Isotope Beams (FRIB), which seeks to produce many exotic, neutron-rich isotopes (nuclei with fixed proton number and varying neutron number) and measure new data to better understand the areas mentioned above. \textcolor{red}{Talk about nuclear chart figure below (need to add figure).} Facilities must use reactions to produce and study short-lived exotic nuclei.
\\

@@

One such technique is to introduce a complex potential as an effective projectile-nucleus interaction to account for refraction and absorption of the incident particles. These complex potentials are called optical potentials. The term optical comes from an analogy where a complex index of refraction is used to describe light refraction and absorption. In nuclear scattering, refraction corresponds to elastic scattering whereas absorption corresponds to flux disappearing to inelastic channels. Optical potentials have been used to calculate observables of many direct reaction processes and play an important role in the development of nuclear reaction theory \cite{thompson_nunes_2009}.
\\

Originally, optical potentials were constrained by data, that is, phenomenological models. Progress in effective field theory (EFT) and renormalization group methods (SRG) have led to a wealth of knowledge on the fundamental interaction between nucleons \cite{Epelbaum:2008ga}. These methods are referred to as \textit{ab initio} or microscopic approaches. We now have access to microscopic optical potentials where the interaction between two nucleons (NN force or interaction) is used in place of phenomenological models offering more predictive power for rare isotopes out of experimental reach.
\\

This paper is organized as follows: in Section \ref{sec:formalism} we present the nuclear optical potential as derived by Feshbach several decades ago \cite{Feshbach:1958nx, Feshbach:1962ut}. We give a basic idea of optical potentials conceptually and how they can be used to calculate observable quantities. Section \ref{sec:phenomenology} gives an overview of phenomenological optical potentials and some recent results \cite{Koning:2003zz}. In Section \ref{sec:microscopic} we discuss two \textit{ab initio} approaches to constructing optical potentials and the successes and limitations of these models. Lastly, we summarize and discuss future topics in Section \ref{sec:conclusion}.

@@

First, we present the optical potential for an $A+1$ particle system consisting of an incident nucleon and a target nucleus of mass number $A$ as derived in \cite{Feshbach:1958nx}. The system is described by the Schr\"odinger equation
%
\begin{eqnarray}
	\label{eq:schrodinger_equation}
	\mathcal{H} \Psi = E \Psi,
\end{eqnarray}
%
with the Hamiltonian $\mathcal{H}$ given below:
%
\begin{eqnarray}
	\label{eq:total_hamiltonian}
	\mathcal{H} = H_A(\textbf{r}_1, \cdots , \textbf{r}_A) + T_0 + V(\textbf{r}_0, \cdots , \textbf{r}_A).
\end{eqnarray}
%
The variables $\textbf{r}_k$ correspond to position, spin, and isospin for the incident nucleon ($k=0$) and each nucleon in the target nucleus ($k=1 \cdots A$). $T_0$ is the kinetic energy of the incident nucleon and $V$ is the potential energy of the $A+1$ system. $H_A$ is the Hamiltonian for the target nucleus and satisfies the Schr\"odinger equation
%
\begin{eqnarray}
	\label{eq:nuclear_schrodinger_equation}
	H_A(\textbf{r}_1, \cdots , \textbf{r}_A) \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A) = \epsilon_i \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A),
\end{eqnarray}
%
for nuclear wave functions $\psi_i$ and energies $\epsilon_i$. Here, the index $i$ corresponds to each state of the target nucleus with $i=0$ being the ground state. The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we can expand the wave function $\Psi$ as follows:
%
\begin{eqnarray}
	\label{eq:wave_function}
	\Psi(\textbf{r}_0, \cdots , \textbf{r}_A) = \sum_{i} \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A) u_i(\textbf{r}_0).
\end{eqnarray}
%
Note, the factors $u_i$ carry the $\textbf{r}_0$ dependence. 
\\

In the following, we suppress the coordinate, spin, and isospin dependencies for brevity. We substitute (\ref{eq:wave_function}) into the Schr\"odinger equation \ref{eq:schrodinger_equation} and use the orthonormality of $\psi_i$ to derive a system of equations for the amplitudes $u_i$:
%
\begin{eqnarray}
	\label{eq:u_equation}
	(T_0 + V_{ii} + \epsilon_i - E) u_i = - \sum_{j \neq i} V_{ij} u_j,
\end{eqnarray}
%
where the potential matrix elements are
%
\begin{eqnarray}
	\label{eq:potential_matrix_elements}
	V_{ij}(\textbf{r}_0) = \int{d^3 r_1 d^3 r_2 \cdots d^3 r_A \psi_i^* V \psi_j}.
\end{eqnarray}
%
Next, we would like to derive an uncoupled equation for $u_0$ to describe elastic scattering in which the target nucleus is in its ground state with an incident nucleon of energy $E$. The other indices $i$ describe an emergent nucleon in a different state (e.g. energy, spin, isospin, etc.) from the incident nucleon. It is convenient to define the vectors
%
\begin{eqnarray}
	\label{eq:u_vector}
	\Phi \equiv
	\begin{pmatrix}
		u_1 \\
		u_2 \\
		\vdots \\
	\end{pmatrix}
	,
\end{eqnarray}
%
\begin{eqnarray}
	\label{eq:potential_vector}
	\textbf{V}_0 =
	\begin{pmatrix}
		V_{01}, V_{02}, \cdots
	\end{pmatrix}
	,
\end{eqnarray}
%
and the matrix operator $\textbf{H}$
%
\begin{eqnarray}
	\label{eq:hamiltonian_operator}
	H_{ij} = T_0 \delta_{ij} + V_{ij} + \epsilon_i \delta_{ij}.
\end{eqnarray}
%
Then we can rewrite (\ref{eq:u_equation}) as
%
\begin{subequations}
	\label{eq:u_vector_equation}
	\begin{eqnarray}
		\label{eq:u_vector_equation_a}
		(T_0 + V_{00} - E) u_0 = -\textbf{V}_0 \Phi,
	\end{eqnarray}
	\begin{eqnarray}
		\label{eq:u_vector_equation_b}
		(\textbf{H}-E) \Phi = -\textbf{V}_0^{\dagger} u_0.
	\end{eqnarray}
\end{subequations}
%
We solve (\ref{eq:u_vector_equation_b}) for $\Phi$
%
\begin{eqnarray}
	\label{eq:phi}
	\Phi = \frac{1}{E - \textbf{H} + i \eta} \textbf{V}_0^{\dagger} u_0,
\end{eqnarray}
%
where $\eta \rightarrow 0^+$ to ensure only outgoing waves are present in exit channels for $u_i$ with $i \geq 1$. Lastly, we substitute $\Phi$ into (\ref{eq:u_vector_equation_a}) to give
%
\begin{eqnarray}
	\label{eq:u0_equation}
	(T_0 + V_{00}  - \textbf{V}_0 \frac{1}{E-\textbf{H}+i\eta} \textbf{V}_0^{\dagger} - E) u_0 = 0,
\end{eqnarray}
%
and define the optical potential as
%
\begin{eqnarray}
	\label{eq:optical_potential}
	V_{opt} = V_{00}  - \textbf{V}_0 \frac{1}{E-\textbf{H}+i\eta} \textbf{V}_0^{\dagger}.
\end{eqnarray}
%
\\

We can see from Eq.~(\ref{eq:optical_potential}) that the optical potential is complex and energy dependent. The factor of $i \eta$ leads to $V_{opt}$ being complex, and thus, non-hermitian. The factor of $i \eta$ accounts for incident particles leaving the entrance channel $u_0$ to an exit channel $u_i$ where $i \geq 1$. This only occurs if reactions are possible, that is, $E > \epsilon_1$. Because $V_{opt}$ is non-hermitian, the $S$-matrix is not unitary giving rise to complex scattering phase shifts. Furthermore, the potential is non-local from the second term. The effective potential depends on the wave function throughout a surrounding region; mathematically, this corresponds to a potential $V(\textbf{r})$ being replaced by $\int d^3 r' \, V(\textbf{r}, \textbf{r}')$ \cite{Hodgson:1971ab}. The derivation only accounts for one nucleon in the exit channel, and thus, does not describe all types of reactions. Feshbach generalized the approach by using projection operators in \cite{Feshbach:1962ut} which is summarized below.
\\

Here, we define the two projection operators $P$ and $Q$. $P$ projects the total wave function onto the ground state part of the target wave function: $P \Psi = \psi_0 u_0$. $Q$ projects onto all other states and is given by $Q = 1-P$. The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, $Q^2 = Q$, and $P Q = 0$. We act on Eq.~(\ref{eq:schrodinger_equation}) with $P$ and $Q$ and use the projection operator relations to obtain two equations:
%
\begin{subequations}
	\label{eq:intermediate_effective_hamiltonian_equations}
	\begin{eqnarray}
		\label{eq:pp_pq}
		(E - \mathcal{H}_{PP}) P \Psi = \mathcal{H}_{PQ} Q \Psi,
	\end{eqnarray}
	\begin{eqnarray}
		\label{eq:qq_qp}
		(E - \mathcal{H}_{QQ}) Q \Psi = \mathcal{H}_{QP} P \Psi.
	\end{eqnarray}
\end{subequations}
%
Solving (\ref{eq:qq_qp}) for $Q \Psi$ yields
%
\begin{eqnarray}
	\label{eq:q_psi}
	Q \Psi = \frac{1}{E - \mathcal{H}_{QQ} + i \eta} \mathcal{H}_{QP} P \Psi.
\end{eqnarray}
%
Substituting $Q \Psi$ into Eq.~(\ref{eq:pp_pq}) and rearranging gives
%
\begin{eqnarray}
	\label{eq:p_psi}
	(E - \mathcal{H}_{PP} - \mathcal{H}_{PQ} \frac{1}{E - \mathcal{H}_{QQ} + i \eta} \mathcal{H}_{QP}) P \Psi = 0.
\end{eqnarray}
%
By taking the ground state of the target nucleus to be zero, $H_A \psi_0 = 0$,  and using $P = \ket{\psi_0} \bra{\psi_0}$, one can show that Eq. \ref{eq:p_psi} becomes
%
\begin{eqnarray}
	\label{eq:p_psi_optical_potential}
	(E - T - \mel{\psi_0}{V}{\psi_0} - \mel{\psi_0}{V Q \frac{1}{E - \mathcal{H}_{QQ} + i \eta} Q V}{\psi_0}) u_0 = 0,
\end{eqnarray}
%
similar to Eq. \ref{eq:u0_equation}. We identify the optical potential as
%
\begin{eqnarray}
	\label{eq:optical_potential_projection}
	V_{opt} = \mel{\psi_0}{V}{\psi_0} + \mel{\psi_0}{V Q \frac{1}{E - \mathcal{H}_{QQ} + i \eta} Q V}{\psi_0},
\end{eqnarray}
% 
where the first term corresponds to pure elastic scattering, and the second term corresponds to virtual nuclear excitations and de-excitations back to the elastic channel.
% Comment: add transition to next section here. Make concluding remarks.

@@

Historically, phenomenological optical potentials have been obtained by fitting elastic-scattering angular distributions with a complex potential of the form
%
\begin{eqnarray}
	\label{eq:phenomenological_optical_potential}
	V_{opt}(r) &=& V_C - V f(x_0) + (\frac{\hbar}{m_{\pi} c})^2 V_{SO}(\bm{\sigma} \cdot \textbf{l}) \frac{1}{r} \frac{d}{dr} f(x_{SO}) \nonumber \\ 
& &- i [W f(x_W) - 4 W_D \frac{d}{dx_D} f(x_D)].
\end{eqnarray}
%
The first term, $V_C$, accounts for charged-interactions between charged particles (e.g. an incident proton and a nuclear target with total charge $Z'$) where
%
\begin{eqnarray}
	\label{eq:coulomb_potential}
	V_C =
	\begin{cases}
		\frac{Z Z' e^2}{r} \qquad \text{if $r \geq R_C$} \\
		\frac{Z Z' e^2}{2 R_C} (3 - \frac{r^2}{R_C^2}) \qquad \text{if $r \leq R_C$},
	\end{cases}
\end{eqnarray}
%
and $R_C = r_C A^{1/3}$ is the nuclear radius. Nuclear radii are roughly proportional to $A^{1/3}$, hence the form of $R_C$. Here, $V_C$ is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$. Note, this term is zero if the projectile particles are neutral; for instance, incident neutrons.
\\

The remaining terms include Woods-Saxon form factors $f(x_i)$ where $x_i = \frac{r-r_i A^{1/3}}{a_i}$ with radius and diffusivity parameters $r_i$ and $a_i$, respectively. Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, thus Woods-Saxon form factors serve as good candidates for modeling the projectile-nucleus interaction. The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV. $V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle and is important for describing analyzing powers.
% Comment: explain what analyzing powers are.
\\

At higher energies, an imaginary component is necessary to describe absorption where particles penetrate into and through the target nucleus without losing energy. The first term, $W$, represents volume absorption, and the second, $W_D$, surface absorption. These components include a Woods-Saxon form factor and its derivative, respectively. Note, the derivative of the Woods-Saxon function peaks at the nuclear radius, hence the $W_D$ accounting for surface absorption. At lower energies ($E < 10$ MeV) the surface term dominates while at higher energies one must include the volume absorption component.
% Comment: mention $W_{SO}$ term.
\\

@@

Lastly, the local-fit models are a combination of the former methods. Here, parameters are specific to a given target nucleus with energy-dependence expressed analytically. The parameters are fit by varying them around global-fit parameters for each nucleus of interest. The resulting parameters are similar for neighboring nuclei; however, the variation in parameters is still unpredictable. \textcolor{red}{Give example of local-fit optical model from Koning with a figure.}
\\

\textcolor{red}{Summarize limitations of phenomenological optical models.} In the next section, we discuss microscopic optical potentials which seek to overcome the shortcomings of the phenomenological models.
\\

References: \cite{Dickhoff:2018wdd}, \cite{Perey:1976zz}, \cite{Koning:2003zz}.

@@

In this section, we present two methods to calculate microscopic optical potentials: the multiple scattering approach and nucleon self-energy methods. As mentioned before, it is important to have a theoretical grasp on applying microscopic NN potentials to the optical potential methodology in order to make predictions where no experimental data are available. Groups have attempted to fit global optical potentials to accomplish this goal but fail to consistently match experimental observables across several nuclei and energies primarily because of the lack of nuclear structure inputs to their models. Recently, a number of methods have been successful in calculating microscopic optical potentials (\textcolor{red}{add references here}).
\\

% Multiple-scattering approach

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% File: candidacy_paper.tex
%
% Author: A. J. Tropiano (tropiano.4@osu.edu)
% Date: July 1, 2019
%
% Candidacy paper on the status of nuclear optical potentials and future prospects.
%
% Revision history:
% 	07/02/19 --- Starting with bulleted outline.
%     07/10/19 --- Adding equations to formalism section.
%	07/11/19 --- Put theoretical issues section as part of the conclusion. Also, wrote much of the formalism section.
%	07/15/19 --- Wrote the phenomenology section.
%	07/17/19 --- Wrote the introduction section.
%	07/19/19 --- Wrote microscopic optical potentials section.
%	07/25/19 --- Revised draft from introduction through multiple-scattering approach.
%	07/26/19 --- Revised nucleon self-energy section and wrote conclusion.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Nuclear reactions are central to many areas of physics. A good understanding of these processes is necessary to answer questions such as the origin of the heavy elements in the universe, fundamental symmetries, or the limits of nuclear stability. For example, half of the neutron-rich atomic nuclei past iron on the periodic table are created by the rapid neutron-capture process known as the r-process which involves a series of nuclear reactions even with nuclei that have never been experimentally produced. Construction of an ``r-process laboratory'' is underway, the Facility for Rare Isotope Beams (FRIB), which seeks to produce many exotic, neutron-rich isotopes (isotopes are nuclei with fixed proton number and varying neutron number) and measure new data to better understand the areas mentioned above. Fig.~\ref{fig:nuclear_chart_2018} shows nuclei with the neutron number N on the x-axis and the proton number Z on the y-axis with stable nuclei as black squares. The r-process takes place below the line of stability with exotic, neutron-rich nuclei, which is the region where FRIB is expected to make substantial progress. It is critical to understand nuclear reactions since facilities must use reactions to produce and study short-lived exotic nuclei.
\\

@@

%
\begin{figure}
	\captionsetup{singlelinecheck=false,justification=raggedright}
	\centering
	\includegraphics[width=14cm]{nuclear_chart_2018}
	\caption{Chart of nuclides with neutron number N counted horizontally and proton number Z counted vertically. The green squares correspond to experimentally observed nuclei, whereas the green shaded region depicts the theoretical limits for each isotope. Blue squares correspond to theoretical calculations by \textit{ab initio} methods which will be discussed later. (Figure from H. Hergert.)}
	\label{fig:nuclear_chart_2018}
\end{figure}
%

One such technique is to introduce a complex potential as an effective projectile-nucleus interaction to account for refraction and absorption of the incident particles. These complex potentials are called optical potentials. The term optical comes from an analogy where a complex index of refraction is used to describe light refraction and absorption. In nuclear scattering, refraction corresponds to elastic scattering and absorption corresponds to flux disappearing to inelastic channels. Optical potentials have been used to calculate observables of many direct reaction processes and play an important role in the development of nuclear reaction theory \cite{thompson_nunes_2009}.
\\

Originally, optical potentials were constrained by nuclear scattering data to compute effective projectile-nucleus potentials. These phenomenological models are parametrized by fitting scattering observables with parameters such as nuclear radii, diffusivity, etc. Progress in effective field theory (EFT) and renormalization group (RG) methods have led to a wealth of knowledge on the fundamental interaction between nucleons \cite{Epelbaum:2008ga}. We now have access to optical potentials where the interaction between two nucleons (NN force or interaction) is used to compute an effective potential. These potentials are called \textit{ab initio} or microscopic optical potentials. Since microscopic models rely less on scattering data, they offer more predictive power for rare isotopes out of experimental reach.
% Comment: say anything about blue squares in chart?
\\

This paper is organized as follows: in Sec.~\ref{sec:formalism} we present the nuclear optical potential as derived by Feshbach several decades ago \cite{Feshbach:1958nx, Feshbach:1962ut}. We give a basic idea of optical potentials conceptually and how they can be used to calculate observable quantities. Sec.~\ref{sec:phenomenology} gives an overview of phenomenological optical potentials and some recent results \cite{Koning:2003zz}. In Sec.~\ref{sec:microscopic} we discuss two \textit{ab initio} approaches to constructing optical potentials and the successes and limitations of these models. Lastly, we summarize and discuss future topics in Sec.~\ref{sec:conclusion}.

@@

First, we present the optical potential for an $A+1$ particle system consisting of an incident nucleon and a target nucleus of mass number $A$ as derived in \cite{Feshbach:1958nx}. The system is described by the Schr\"odinger equation
%
\begin{eqnarray}
	\label{eq:schrodinger_equation}
	\mathcal{H} \Psi = E \Psi,
\end{eqnarray}
%
with the Hamiltonian $\mathcal{H}$ given below:
%
\begin{eqnarray}
	\label{eq:total_hamiltonian}
	\mathcal{H} = H_A(\textbf{r}_1, \cdots , \textbf{r}_A) + T_0 + V(\textbf{r}_0, \cdots , \textbf{r}_A).
\end{eqnarray}
%
The variables $\textbf{r}_k$ correspond to position, spin, and isospin for the incident nucleon ($k=0$) and each nucleon in the target nucleus ($k=1 \cdots A$). $T_0$ is the kinetic energy of the incident nucleon and $V$ is the potential energy of the $A+1$ system. $H_A$ is the Hamiltonian for the target nucleus and satisfies the Schr\"odinger equation
%
\begin{eqnarray}
	\label{eq:nuclear_schrodinger_equation}
	H_A(\textbf{r}_1, \cdots , \textbf{r}_A) \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A) = \epsilon_i \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A),
\end{eqnarray}
%
for nuclear wave functions $\psi_i$ and energies $\epsilon_i$. Here, the index $i$ corresponds to each state of the target nucleus with $i=0$ being the ground state. The nuclear wave functions $\psi_i$ form a complete, orthonormal set; thus, we can expand the wave function $\Psi$ as follows:
%
\begin{eqnarray}
	\label{eq:wave_function}
	\Psi(\textbf{r}_0, \cdots , \textbf{r}_A) = \sum_{i} \psi_i(\textbf{r}_1, \cdots , \textbf{r}_A) u_i(\textbf{r}_0).
\end{eqnarray}
%
Note, the expansion coefficients $u_i$ carry the $\textbf{r}_0$ dependence. Physically, the expansion coefficients correspond to different outgoing channels with $u_0$ representing elastic scattering.
\\

In the following, we suppress the coordinate, spin, and isospin dependencies for brevity. We substitute (\ref{eq:wave_function}) into the Schr\"odinger equation (\ref{eq:schrodinger_equation}) and use the orthonormality of $\psi_i$ to derive a system of equations for the expansion coefficients $u_i$:
%
\begin{eqnarray}
	\label{eq:u_equation}
	(T_0 + V_{ii} + \epsilon_i - E) u_i = - \sum_{j \neq i} V_{ij} u_j,
\end{eqnarray}
%
where the potential matrix elements are
%
\begin{eqnarray}
	\label{eq:potential_matrix_elements}
	V_{ij}(\textbf{r}_0) = \int{d^3 r_1 d^3 r_2 \cdots d^3 r_A \psi_i^* V \psi_j}.
\end{eqnarray}
%
Next, we would like to derive an uncoupled equation for $u_0$ to describe elastic scattering in which the target nucleus is in its ground state with an incident nucleon of energy $E$. The other indices $i$ describe an emergent nucleon in a different state (e.g. energy, spin, isospin, etc.) from the incident nucleon. It is convenient to define the vectors
%
\begin{eqnarray}
	\label{eq:u_vector}
	\Phi \equiv
	\begin{pmatrix}
		u_1 \\
		u_2 \\
		\vdots \\
	\end{pmatrix}
	,
\end{eqnarray}
%
\begin{eqnarray}
	\label{eq:potential_vector}
	\textbf{V}_0 =
	\begin{pmatrix}
		V_{01}, V_{02}, \cdots
	\end{pmatrix}
	,
\end{eqnarray}
%
and the matrix operator $\textbf{H}$
%
\begin{eqnarray}
	\label{eq:hamiltonian_operator}
	H_{ij} = T_0 \delta_{ij} + V_{ij} + \epsilon_i \delta_{ij},
\end{eqnarray}
%
for $i$, $j > 0$. Then we can rewrite (\ref{eq:u_equation}) as
%
\begin{subequations}
	\label{eq:u_vector_equation}
	\begin{eqnarray}
		\label{eq:u_vector_equation_a}
		(T_0 + V_{00} - E) u_0 = -\textbf{V}_0 \Phi,
	\end{eqnarray}
	\begin{eqnarray}
		\label{eq:u_vector_equation_b}
		(\textbf{H}-E) \Phi = -\textbf{V}_0^{\dagger} u_0.
	\end{eqnarray}
\end{subequations}
%
We solve (\ref{eq:u_vector_equation_b}) for $\Phi$
%
\begin{eqnarray}
	\label{eq:phi}
	\Phi = \frac{1}{E - \textbf{H} + i \eta} \textbf{V}_0^{\dagger} u_0,
\end{eqnarray}
%
where $\eta \rightarrow 0^+$ to ensure only outgoing waves are present in exit channels for $u_i$ with $i \geq 1$. Lastly, we substitute $\Phi$ into (\ref{eq:u_vector_equation_a}) to give
%
\begin{eqnarray}
	\label{eq:u0_equation}
	(T_0 + V_{00}  - \textbf{V}_0 \frac{1}{E-\textbf{H}+i\eta} \textbf{V}_0^{\dagger} - E) u_0 = 0,
\end{eqnarray}
%
and define the optical potential as
%
\begin{eqnarray}
	\label{eq:optical_potential}
	V_{opt} = V_{00}  - \textbf{V}_0 \frac{1}{E-\textbf{H}+i\eta} \textbf{V}_0^{\dagger}.
\end{eqnarray}
%
\\

We can see from Eq.~(\ref{eq:optical_potential}) that the optical potential is complex and energy dependent. The factor of $i \eta$ leads to $V_{opt}$ being complex, and thus, non-hermitian. The factor of $i \eta$ accounts for incident particles leaving the entrance channel $u_0$ to an exit channel $u_i$ where $i \geq 1$. This only occurs if reactions are possible, that is, $E > \epsilon_1$. Because $V_{opt}$ is non-hermitian, the $S$-matrix is not unitary giving rise to complex scattering phase shifts. Furthermore, the potential is non-local from the second term. We can see the non-locality by acting the operator $V_{opt}$ on a wave function $\Psi$ in coordinate-space, giving an integral over the surrounding region. Mathematically, this corresponds to a term $\int d^3 r' \, V(\textbf{r}, \textbf{r}') \Psi(\textbf{r}')$ in the Schr\"odinger equation \cite{Hodgson:1971ab}. The derivation only accounts for one nucleon in the exit channel, and thus, does not describe all types of reactions. Feshbach generalized the approach by using projection operators in \cite{Feshbach:1962ut} which is summarized below.
\\

Here, we define the two projection operators $P$ and $Q$. $P$ projects the total wave function onto the ground state part of the target wave function: $P \Psi = \psi_0 u_0$. $Q$ projects onto all other states and is given by $Q = 1-P$. The projection operators satisfy the following relations: $P+Q=1$, $P^2 = P$, $Q^2 = Q$, and $P Q = 0$. We act on Eq.~(\ref{eq:schrodinger_equation}) with $P$ and $Q$ and use the projection operator relations to obtain two equations:
%
\begin{subequations}
	\label{eq:intermediate_effective_hamiltonian_equations}
	\begin{eqnarray}
		\label{eq:pp_pq}
		(E - \mathcal{H}_{PP}) P \Psi = \mathcal{H}_{PQ} Q \Psi,
	\end{eqnarray}
	\begin{eqnarray}
		\label{eq:qq_qp}
		(E - \mathcal{H}_{QQ}) Q \Psi = \mathcal{H}_{QP} P \Psi,
	\end{eqnarray}
\end{subequations}
%
where $\mathcal{H}_{PP}$ refers to $P \mathcal{H} P$ and so forth. Solving (\ref{eq:qq_qp}) for $Q \Psi$ yields
%
\begin{eqnarray}
	\label{eq:q_psi}
	Q \Psi = \frac{1}{E - \mathcal{H}_{QQ} + i \eta} \mathcal{H}_{QP} P \Psi.
\end{eqnarray}
%
Substituting $Q \Psi$ into Eq.~(\ref{eq:pp_pq}) and rearranging gives
%
\begin{eqnarray}
	\label{eq:p_psi}
	(E - \mathcal{H}_{PP} - \mathcal{H}_{PQ} \frac{1}{E - \mathcal{H}_{QQ} + i \eta} \mathcal{H}_{QP}) P \Psi = 0.
\end{eqnarray}
%
By taking the ground state of the target nucleus to be zero, $H_A \psi_0 = 0$,  and using $P = \ket{\psi_0} \bra{\psi_0}$, one can show that Eq.~(\ref{eq:p_psi}) becomes
%
\begin{eqnarray}
	\label{eq:p_psi_optical_potential}
	(E - T - \mel{\psi_0}{V}{\psi_0} - \mel{\psi_0}{V Q \frac{1}{E - \mathcal{H}_{QQ} + i \eta} Q V}{\psi_0}) u_0 = 0,
\end{eqnarray}
%
similar to Eq.~(\ref{eq:u0_equation}). We identify the optical potential as
%
\begin{eqnarray}
	\label{eq:optical_potential_projection}
	V_{opt} = \mel{\psi_0}{V}{\psi_0} + \mel{\psi_0}{V Q \frac{1}{E - \mathcal{H}_{QQ} + i \eta} Q V}{\psi_0},
\end{eqnarray}
% 
where the first term corresponds to pure elastic scattering, and the second term corresponds to virtual nuclear excitations and de-excitations back to the elastic channel. Note, this is technically the same as Eq.~(\ref{eq:optical_potential}), as the inner products are written out explicitly in Eq.~(\ref{eq:optical_potential_projection}) and denoted with subscripts in Eq.~(\ref{eq:optical_potential}). Also, the two vector terms $\textbf{V}_0$ in the original equation accounts for couplings of the elastic channel to inelastic channels, while this is done with the $Q$ projection operator in the second definition of the optical potential.
% Comment: concluding remarks or transition?

@@

Historically, phenomenological optical potentials have been obtained by fitting elastic-scattering angular distributions with a complex potential of the form \cite{Perey:1976zz, Dickhoff:2018wdd}
%
\begin{eqnarray}
	\label{eq:phenomenological_optical_potential}
	V_{opt}(r, E) &=& V_C(r) - V(E) f(x_0) + (\frac{\hbar}{m_{\pi} c})^2 V_{SO}(E, \bm{\sigma} \cdot \textbf{l}) \frac{1}{r} \frac{d}{dr} f(x_{SO}) \nonumber \\ 
& &- i [W(E) f(x_W) - 4 W_D(E) \frac{d}{dx_D} f(x_D)].
\end{eqnarray}
% Comment: how is this related to nuclear density or probability of finding a nucleon in the nucleus?
%
The first term, $V_C$, accounts for charged-interactions between charged particles (e.g. an incident proton and a nuclear target with total charge $Z'$) where
%
\begin{eqnarray}
	\label{eq:coulomb_potential}
	V_C =
	\begin{cases}
		\frac{Z Z' e^2}{r} \qquad \text{if $r \geq R_C$} \\
		\frac{Z Z' e^2}{2 R_C} (3 - \frac{r^2}{R_C^2}) \qquad \text{if $r \leq R_C$},
	\end{cases}
\end{eqnarray}
%
and $R_C = r_C A^{1/3}$ is the nuclear radius. Nuclear radii are roughly proportional to $A^{1/3}$, hence the form of $R_C$. Here, $V_C$ is the Coulomb potential of a spherical, uniformly-charged distribution of radius $R_C$. Note, this term is zero if the projectile particles are neutral; for instance, incident neutrons.
\\

The remaining terms include Woods-Saxon form factors $f(x_i)$ where $x_i = \frac{r-r_i A^{1/3}}{a_i}$ with radius and diffusivity parameters $r_i$ and $a_i$, respectively. Woods-Saxon potentials have been used to describe the mean field potential of a nucleon in a nucleus, thus Woods-Saxon form factors serve as good candidates for modeling the projectile-nucleus interaction. (A mean field potential is a potential that averages over the interactions of a system reducing a many-body problem to a one-body problem.) The $V$ term gives the approximate interaction between the incident particle and the target nucleus and typically has a potential well depth of $V \approx 50$ MeV. $V_{SO}$ is the spin-orbit coupling term where $\bm{\sigma}$ is the spin operator and $\bm{l}$ is the angular momentum of the incident particle and is important for describing analyzing powers (scattering observables related to spin-dependent cross sections).
\\

At higher energies, an imaginary component is necessary to describe absorption where particles penetrate into and through the target nucleus. The first term, $W$, represents volume absorption, and the second, $W_D$, surface absorption. These components include a Woods-Saxon form factor and its derivative, respectively. Note, the derivative of the Woods-Saxon function peaks at the nuclear radius, hence the $W_D$ accounting for surface absorption. At lower energies ($E < 10$ MeV) the surface term dominates while at higher energies one must include the volume absorption component. In Fig.~\ref{fig:potential_wells_omp}, we show examples of the energy dependent terms in Eq.~\ref{eq:phenomenological_optical_potential}.
\\

%
\begin{figure}
	\captionsetup{singlelinecheck=false,justification=raggedright}
	\centering
	\includegraphics[width=10cm]{potential_wells_omp}
	\caption{Potential well depths as a function of laboratory energy $E$ for each of the terms in Eq.~\ref{eq:phenomenological_optical_potential} including an imaginary spin-orbit term, $W_{SO}$. (Figure from \cite{Koning:2003zz}.)}
	\label{fig:potential_wells_omp}
\end{figure}
%

@@

Lastly, the local-fit models are a combination of the former methods. Here, parameters are specific to a given target nucleus with energy-dependence expressed analytically. The parameters are fit by varying them around global-fit parameters for each nucleus of interest. The resulting parameters are similar for neighboring nuclei; however, the variation in parameters is still unpredictable. An example of a recent local-fit optical potential is given in \cite{Koning:2003zz}.
\\

Phenomenological models have been successful in describing scattering from nuclei where data are available; however, the approach lacks realistic nuclear structure inputs like multi-pion exchange contributions, three-body interactions, etc. Without including these details, phenomenological models cannot make consistent predictions across all scattering systems or extend to exotic nuclei. Furthermore, there is no reliable way to quantify uncertainty in these models. In the next section, we discuss microscopic optical potentials which seek to overcome the shortcomings of the phenomenological models.

@@

In this section, we present two methods to calculate microscopic optical potentials: the multiple scattering approach and nucleon self-energy methods. As mentioned before, it is important to have a theoretical grasp on applying microscopic NN potentials to the optical potential methodology in order to make predictions where no experimental data are available. Groups have attempted to fit global optical potentials to accomplish this goal but fail to consistently match experimental observables across several nuclei and energies primarily because of the lack of nuclear structure inputs to their models. Recently, a number of methods have been successful in calculating microscopic optical potentials \cite{Furumoto:2019anr, Idini:2019hkq, Rotureau:2016jpf}.

%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Multiple-scattering approach}
\label{sec:multiple_scattering}
